Supplemental Information

### 2021-05-11 analysis/metabolomics.Rmd
move analysis out of inst to top-level directory

```{r}
withr::with_dir(here::here(), {
  raw <- tar_read(metab_targeted_raw)
  clean <- tar_read(metab_targeted_clean)
  metab_pca <- tar_read(metab_targeted_pca)
  metab_limma <- tar_read(metab_targeted_limma)
  # metab_tt <- tar_read(metab_different_differences)
  volcano <- tar_read(metab_volcano)
})
```

@@

```{r}
plot_mois(clean, "malate")
```

>>>>

```{r}
withr::with_dir(here::here(), {
  raw <- tar_read(metab_targeted_raw)
  clean <- tar_read(metab_targeted_clean)
  metab_pca <- tar_read(metab_targeted_pca)
  metab_limma <- tar_read(metab_targeted_limma)
  tt <- tar_read(metab_different_differences)
  volcano <- tar_read(metab_volcano)
  msea <- tar_read(msea_plot)
  leading_edge <- tar_read(leading_edge)
})
```

@@

## Metabolite set enrichment

```{r}
msea
```

```{r}
leading_edge
```

### 2021-05-11 manuscript/manuscript.Rmd
move analysis out of inst to top-level directory

# kable function
my_kable <- function(data, ...) {
  kableExtra::kable(data, booktabs = TRUE, linesep = "", ...) %>% 
    kableExtra::kable_styling(latex_options = c("HOLD_position"), font_size = 11)
}

withr::with_dir(here::here(), {
  biomass <- targets::tar_read(biomass)
  resources <- targets::tar_read(resources_table)
  figs <- targets::tar_load(targets::matches("m\\d_figure"))
})

biomass <- tibble::deframe(biomass)
```

>>>>

biomass <- targets::tar_read(biomass)
resources <- targets::tar_read(resources_table)
figs <- targets::tar_load(targets::matches("m\\d_figure"))
biomass <- tibble::deframe(biomass)
```

### 2021-05-11 manuscript/supplement.Rmd
move analysis out of inst to top-level directory

# kable function
my_kable <- function(data, ...) {
  kableExtra::kable(data, booktabs = TRUE, linesep = "", ...) %>% 
    kableExtra::kable_styling(latex_options = c("HOLD_position"), font_size = 11)
}

withr::with_dir(here::here(), {
  hyp <- targets::tar_read(lf_hypoxia_table)
  bay <- targets::tar_read(lf_bay_table)
  pasmc <- targets::tar_read(pasmc_hypoxia_table)
  figs <- targets::tar_load(targets::matches("s\\d_figure"))
})

```

>>>>

hyp <- targets::tar_read(lf_hypoxia_table)
bay <- targets::tar_read(lf_bay_table)
pasmc <- targets::tar_read(pasmc_hypoxia_table)
figs <- targets::tar_load(targets::matches("s\\d_figure"))
```
